A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Add events information

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/side-effects.tex}
\input{tag/analysisStable.tex}
\input{tag/enrichDataset.tex}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\newcommand{\local}{\texttt{local}\xspace}
\newcommand{\unlockBinding}{\texttt{unlockBinding}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\newcommand{\datatable}{\texttt{data.table}\xspace}
\newcommand{\base}{\texttt{base}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

%%In the corpus, we observe \AllEventCountRnd events. Only \EvalEventCountRnd
%%events occur inside eval. This is just \EvalEventAllPerc of all events.
%%Figure~\ref{fig:event-distribution} shows the distribution of events for
%%core and package \eval calls.

{\bf Missing from this section is the measure of the number of events
  happening in an eval}

>>>>

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/side-effects.tex}
\input{tag/events.tex}
\input{tag/analysisStable.tex}
\input{tag/enrichDataset.tex}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\newcommand{\local}{\texttt{local}\xspace}
\newcommand{\unlockBinding}{\texttt{unlockBinding}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\newcommand{\datatable}{\texttt{data.table}\xspace}
\newcommand{\mlogit}{\texttt{mlogit}\xspace}
\newcommand{\mboost}{\texttt{mboost}\xspace}
\newcommand{\metafor}{\texttt{metafor}\xspace}
\newcommand{\lavaan}{\texttt{lavaan}\xspace}
\newcommand{\mclust}{\texttt{mclust}\xspace}
\newcommand{\gamlss}{\texttt{gamlss}\xspace}

\newcommand{\base}{\texttt{base}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

We compare the number of events intercepted during execution of \eval across the
whole corpus. For this, we use the number of interpreter's evaluator loops as a
proxy for events. In the corpus, we observe \AllEventCountRnd events. Only
\EvalEventCountRnd events occur inside eval. This is just \EvalEventAllPerc of
all events. Figure~\ref{fig:event-distribution} shows the distribution of events
caused by \eval calls from R Core and CRAN packages.

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{lll}\hline
Events & Core Eval Call \% & Package Eval Call \% \\ \hline
\EventsMinRangeA--\EventsMaxRangeA & \EventsCoreEvalPercA & \EventsPackageEvalPercA \\
\EventsMinRangeB--\EventsMaxRangeB & \EventsCoreEvalPercB & \EventsPackageEvalPercB \\
\EventsMinRangeC--\EventsMaxRangeC & \EventsCoreEvalPercC & \EventsPackageEvalPercC \\
\end{tabular}} \label{table:event-distribution}
\caption{Distribution of events in \eval calls across Core and Package}
\end{table}

We observe a very wide spread in the number of events generated by \eval
calls. The largest number of events generated by an \eval call is \EventsMaxCount.
However majority of \eval calls perform up to \EventsMaxRangeA events.
It is interesting to note that a higher proportion of Core R \eval calls perform
side effects in the \EventsMinRangeB--\EventsMaxRangeB range.
Only \EventsCoreEvalCountC Core R \eval calls and \EventsPackageEvalCountC
package \eval call generate \EventsMinRangeC to \EventsMaxRangeC events.
These \eval calls originate from statistical modeling packages such as \mlogit,
\mboost, \metafor, \lavaan, \mclust and \gamlss.
